%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\labelitemi}{}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1: }{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeCustomSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Junjie Li}} & Email: {junjieli0909@foxmail.com}\\
  & Mobile: +86 156-5103-9915 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education Background}
\resumeSubHeadingListStart
    \resumeSubheading
      {Northwestern University}{Evanston, IL}
      {M.S. in Computer Science;  GPA: 3.86 / 4.00}{Sep. 2015 -- Dec. 2016}
    \resumeSubheading
      {Nanjing University of Posts and Telecommunications}{Nanjing, China}
      {B.E. in Communication Engineering;  GPA: 3.84 / 5.00}{Aug. 2011 -- May. 2015}
    \resumeCustomSubheading {Academic Highlights} {} 
       \resumeItemListStart
        \resumeItem{IEEE Journal Publication} {Personal Access Control System Using Moving Object Detection and Face Recognition}
        \resumeItem{Obtained Dual Degree} {New York Institute of Technology, B.S. in Electrical and Electronics with GPA: 3.56 / 4.00}
       \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart
     % Microsoft Experience
         \resumeSubheading
      {Microsoft. {Cloud and AI, Developer Division}}{Shanghai, CN}
      {Product Manager}{September 2020 - Now}
      \resumeItemListStart
        \resumeItem{General Summary} {Focus on driving developer tool chains for building applications on Microsoft 365 (Office) developer platforms including Teams, Outlook and Office.com}{}
          \resumeItemListStart
            \item {Improving Teams Toolkit (A Visual Studio Code Extension) end to end development experience such as native Azure integration.}
            \item {Lead product design on Command Line tooling to support keyboard-centric experience from ground up.}
            \item {Delivering SDKs to delight developers on simplifying authentications.}
          \resumeItemListEnd
          
      \resumeItemListEnd
     % Trip Experience
         \resumeSubheading
      {Trip.com Group. {Flight Business Unit}}{Shanghai, CN}
      {Product Manager}{August 2018 - September 2020}
      \resumeItemListStart
        \resumeItem{General Summary} {Focus driving product development, feature enhancement and integration with various GDS connections and external partners.}
        \resumeItem{Product lines responsible for and key results}{}
          \resumeItemListStart
            \item {Enhance structured fare condition processing and automated ticket refund/exchange features: Optimized customers' booking experience and reduced operation cost for providing post booking services.}
            \item {Integrate with GDS ancillary service platform: Enrich Trip's after sales functionalities and complete Trip's overall servicing capability as an one-step booking platform.}
            \item {Lead product design of partner portal: a portal for Trip's supplier to manage their air content inventory and access visualized industry data.}
          \resumeItemListEnd
          
        \resumeItem{Day-to-day duties}{}
          \resumeItemListStart
            \item {Requirement Analysis: Analyze existing feature enhancements and new feature requirements from business to operation teams.}
            \item {Product Design: Design product logic and draft function specifications, produce integration workflow with detailed external API research.}
            \item {Project Management: Drive agile development process with engineering team, ensure product delivery and feature iterations in road map.}
            \item {Daily Supervision: Validate product functionalities and API interactions after feature release, monitor key technical and business metrics on daily basis.}
            \item {Team Collaboration: serve as point of contact, ensure communication and collaboration in often cross-company teams.}
          \resumeItemListEnd
      \resumeItemListEnd
    
    % Apple Experience 
    \resumeSubheading
      {Apple, Inc. {Online Store Engineering}}{Sunnyvale, US}
      {Software Development Engineer}{June 2017 - June 2018}
        \resumeItemListStart
        \resumeItem{General Summary} {Part of Checkout Redesign Project to build scalable web services on Apple Online Store to enable global consumers with a smooth and effortless checkout experience.}
          \resumeItemListStart
            \item {Feature developed under Agile mythology using Scala, build UT with Mockito and Power Mock.}
            \item {Refactoring existing Code to apply multiple design pattern like delegate, factory; Ensure thread safety and support high concurrency.}
            \item {Performance Tuning using AspectJ and minimize API/Wire counts to mitigate downstream service pressures.}
            \item {Using Jenkins and InfraRed for build automation, CI/CD.}
        \resumeItemListEnd
      \resumeItemListEnd
      
\resumeSubHeadingListEnd

  
 

% --------Technical SKILLS------------
\section{Programming Skills, languages and Other Skills}
\resumeSubHeadingListStart
    \resumeCustomSubheading{Programming Languages: JAVA, Scala, JavaScript, HTML/CSS, SQL} {}
    \resumeCustomSubheading{Software Skills: MySQL, MATLAB; Latex, Markdown; MS Office} {}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
